---
title: "Database Documentation"
author: "Mai Nguyen"
date: "16 Jul 2019"
output:
  html_document:
    highlight: tango
    number_sections: no
    theme: cerulean
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(pander)
library(tidyr)
```

## Data table

```{r list of table, echo=F}
path = paste(getwd(),"Raw/",sep="")

# Import data
list_tables = list.files(path=path)
```

At this time, there are `r length(list_tables)` tables, include:
```{r table name, echo=F}
table_name = gsub("gonjoy34.","",list_tables)
table_name = gsub(".csv","",table_name)
table_name
```

```{r function to create description for data table, echo = F}
desc_fun = function(nameoftable){
  data_field = names(nameoftable)
  description = rep("",length(data_field))
  table_description=data.frame(cbind(data_field,description))
}
```

### 1. Clients {.tabset}
#### 1.1 User
This table provides information about ...

```{r user table, echo = F}
user = read.csv(paste(path,list_tables[1],sep=""),header=T)
```

```{r write description for user table, echo=F}
user_desc=desc_fun(user)
user_desc$description=c(rep("",dim(user)[2]))
user_desc$description[2]="This is customerID"
pander(head(user_desc))
```

#### 1.2 Provider
```{r provider table, echo = F}
provider = read.csv(paste(path,list_tables[13],sep=""),header=T)
```

```{r write description for provider table, echo=F}
provider_desc=desc_fun(provider)
provider_desc$description=c(rep("",dim(provider)[2]))
provider_desc$description[3]="This is customerID"
pander(head(provider_desc))
```

#### 1.3 Visitors
```{r visitor table, echo = F}
visitors = read.csv(paste(path,list_tables[17],sep=""),header=T)
```

```{r write description for visitor table, echo=F}
visitors_desc=desc_fun(visitors)
visitors_desc$description=c(rep("",dim(visitors)[2]))
visitors_desc$description[1]="This is customerID"
pander(head(visitors_desc))
```
### 2. History {.tabset}
#### 2.1 History location

#### 2.2 History Search

#### 2.3 History NLP
```{r history NLP table, echo = F}
histNLP = read.csv(paste(path,list_tables[3],sep=""),header=T)
```

Data fields of table History NLP are:
```{r write description for history NLP table, echo=F}
histNLP_desc=desc_fun(histNLP)
histNLP_desc$description=c(rep("",dim(histNLP)[2]))
histNLP_desc$description[1]="This is customerID"
names(histNLP)
```

## Data connection
This section describes how data tables are connected.

## Data processing
* describes how to extract information from other tables to obtain dataset for analysis.
* how to clean data
* how to transform data
```{r user table processing, echo=F}
user1=separate(customer,savedAddress,sep=",",into = c("id","channelID","botID","botdesc","conversation","userid","username","url"),remove = F)
user$createdAt=format(user$createdAt,"mm")
```

## Data visualization
```{r visualization customer table, echo=F}

```


